\vspace{-0.25em}\thetitle

### 2009-07-28 paper.tex
...
Add LaTeX for size/ival prediction CDFs.

@@

@@

\subsection{Evaluating Prediction Quality}\sec{evaluation}

@@

>>>>

\subsection{Data Sets}

@@

We model several aspects of flow behavior via feature-frequency linear representation.
Packet sizes and and inter-packet intervals are represented using frequency histograms.
Packet sizes are naturally quantized, taking on only values from 1 to the \caps{MTU}, which was 1500 in all of our traces.

@@

\subsection{Evaluating Predictions}\sec{evaluation}

@@

\begin{figure*}[t!]
\begin{center}
\subfloat[Packet sizes: \footnotesize{DARTMOUTH}]{%
\includegraphics[width=3.545in]{size/dart}}
\subfloat[Packet sizes: \footnotesize{SIGCOMM 2004}]{%
\includegraphics[width=3.545in]{size/sc04}}
\subfloat[Inter-packet intervals: \footnotesize{DARTMOUTH}]{%
\includegraphics[width=3.545in]{ival/dart}}
\subfloat[Inter-packet intervals: \footnotesize{SIGCOMM 2004}]{%
\includegraphics[width=3.545in]{ival/sc04}}
\caption{%
CDFs of Kolmogorov-Smirnov p-values for various predictors of packet size distribution and inter-packet interval distribution for two selected traces. Lower curves are better and the ``ideal'' curve provides a lower bound on quality.
Vertical segments indicate the farthest distance between the ideal and each CDF.
This distance serves as a pessimistic measure of each predictor's error rate.
}
\fig{cdf}
\end{center}
\vspace{-2em}
\end{figure*}
